RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
one word
added comment about caper's comparative.data method

Generating NeXML files from R is likewise straight forward.  Here we
write a phylogeny from the `ape::phylo` format out to a NeXML file:

@@

The first argument to `nexml_write` can be a `phylo` phylogeny,
`multiPhylo` list of phylogenies, or a `nexml` object -- anything that
can be coerced into the `nexml` class.  As we have seen, NeXML files
can contain multiple phylogenetic trees, as well as character matrices.
We can add both trees  and character data using `nexml_write`,

>>>>

Generating NeXML files from R is likewise straightforward.  Here we
write a phylogeny from the `ape::phylo` format out to a NeXML file:

@@

<!-- in caper there is this method comparative.data to join data
and trees on taxon labels. it would be nice if this merged data
structure could also be passed to nexml_write (or should that be
write.nexml?) -->
The first argument to `nexml_write` can be a `phylo` phylogeny,
`multiPhylo` list of phylogenies, or a `nexml` object -- anything that
can be coerced into the `nexml` class.  As we have seen, NeXML files
can contain multiple phylogenetic trees, as well as character matrices.
We can add both trees  and character data using `nexml_write`,
